### 2023-03-02 calculus.tex
Add discussion of alternative conditional rules

The boolean values are straightforward to handle:
%
\begin{mathpar}
  \judgment{ }{
    \ctxSynTypeU{\ctx}{\ETrue}{\TBool}
  }{USTrue}

@@

Conditionals, however, offer an interesting case. In the unmarked language, we have both explicit
synthetic and analytic rules: % TODO intuition why
%
\begin{mathpar}
  \judgment{
    \ctxAnaTypeU{\ctx}{\EMV_1}{\TBool} \\\\
    \ctxSynTypeU{\ctx}{\EMV_2}{\TMV_1} \\
    \ctxSynTypeU{\ctx}{\EMV_3}{\TMV_2}
  }{
    \ctxSynTypeU{\ctx}{\EIf{\EMV_1}{\EMV_2}{\EMV_3}}{\TJoin{\TMV_1}{\TMV_2}}
  }{USIf}

@@

These rules complete the development of the marked lambda calculus for the gradually typed lambda
calculus.

@@

To conclude this section, we present two more metatheorems that help ensure correctness of the
system. Though \cref{thm:calculus-marking-well-formedness} guarantees that marking does not change
the syntactic structure of a program, it makes no statement about the presence of error marks in the
resulting marked program. Following the logic of constructing marking rules, we have
\cref{thm:calculus-marking-well-ill-typed}.

>>>>

The boolean values are straightforward to handle, behaving in a similar manner as numbers: 
%
\begin{mathpar}
  \judgment{ }{
    \ctxSynTypeU{\ctx}{\ETrue}{\TBool}
  }{USTrue}

@@

Conditionals, however, offer an interesting case. In the unmarked language, we have both explicit
synthetic and analytic rules:
%
\begin{mathpar}
  \judgment{
    \ctxAnaTypeU{\ctx}{\EMV_1}{\TBool} \\\\
    \ctxSynTypeU{\ctx}{\EMV_2}{\TMV_1} \\
    \ctxSynTypeU{\ctx}{\EMV_3}{\TMV_2}
  }{
    \ctxSynTypeU{\ctx}{\EIf{\EMV_1}{\EMV_2}{\EMV_3}}{\TJoin{\TMV_1}{\TMV_2}}
  }{USIf}

@@

The framework also allows for other localization approaches. For example, we may regard the first
branch as ``correct'' and localize any errors to the second. The following rule formalizes such a
design:
\[%
  \judgment{
    \ctxAnaFixedInto{\ctx}{\EMV_1}{\ECMV_1}{\TBool} \\
    \ctxSynFixedInto{\ctx}{\EMV_2}{\ECMV_2}{\TMV} \\
    \ctxAnaFixedInto{\ctx}{\EMV_3}{\ECMV_3}{\TMV}
  }{
    \ctxSynFixedInto{\ctx}{\EIf{\EMV_1}{\EMV_2}{\EMV_3}}{\ECIf{\ECMV_1}{\ECMV_2}{\ECMV_3}}{\TMV}
  }{MKSIf'}
\]%
Of course, corresponding unmarked and marked typing rules would follow similar structure, and other
heuristics may be devised for different kinds of branching structures.

@@

\subsubsection{Additional Theorems}
To conclude this section, we present two more metatheorems that help ensure correctness of the
system. Though \cref{thm:calculus-marking-well-formedness} guarantees that marking does not change
the syntactic structure of a program, it makes no statement about the presence of error marks in the
resulting marked program. Following the logic of constructing marking rules, we have
\cref{thm:calculus-marking-well-ill-typed}.
